QALY Comparison - Living Wage Intervention

### 2023-11-06 minos/testing/QALY_comparison_energyCrises_diff.Rmd
New visualisation script for comparing energyDownlift with energyDownliftNoSupport

---
title: "QALY Comparisons - Energy Crisis Interventions"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

# combine the dataframes
combined <- rbind(base, support, noSupport)
```

@@

```{r}
ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'Number Individuals Receiving Intervention')

ggplot(filter(combined, intervention != 'baseline'), aes(x = year, y = total_boost, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'Total Boost amount by year')

@@

# Now change from baseline
combined.QALY.change <- combined %>%
  select(run_id, year, intervention, QALYs) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'QALYs') %>%
  mutate(QALYs_Support = energyDownlift - baseline,
         QALYs_NoSupport = energyDownliftNoSupport - baseline) %>%
  select(run_id, year, QALYs_Support, QALYs_NoSupport) %>%
  pivot_longer(cols = QALYs_Support:QALYs_NoSupport,
               names_prefix = 'QALYs_',
               names_to = 'intervention',
               values_to = 'QALYs')

ggplot(data = combined.QALY.change, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  geom_smooth() +
  labs(title = 'QALY change from Baseline')
```

Can check histogram over each run to see the range of QALYs.

```{r}
# histogram of qalys
ggplot(combined, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  facet_wrap(~year)

ggplot(filter(combined, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'QALYs by run', subtitle = '2022')

ggplot(filter(combined, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'QALYs by run', subtitle = '2028')

ggplot(filter(combined, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'QALYs by run', subtitle = '2034')
```

and histograms of change...

```{r}
# histogram of qalys
ggplot(combined.QALY.change, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  facet_wrap(~year) +
  labs(title = 'QALY change by run', subtitle = 'All Years') +
  xlab('QALY Change')

ggplot(filter(combined.QALY.change, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'QALY change by run', subtitle = '2022') +
  xlab('QALY Change')

ggplot(filter(combined.QALY.change, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'QALY change by run', subtitle = '2028') +
  xlab('QALY Change')

ggplot(filter(combined.QALY.change, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'QALY change by run', subtitle = '2034') +
  xlab('QALY Change')
```

...and SF_12 MCS and PCS for good measure.

```{r}
ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'SF_12_MCS')

ggplot(combined, aes(x = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  facet_wrap(~year) +
  labs(title = 'SF_12_MCS')

ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'SF_12_PCS')

ggplot(combined, aes(x = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  facet_wrap(~year) +
  labs(title = 'SF_12_PCS')
```

@@

```{r}
base.auc <- base %>%
  group_by(run_id) %>%
  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
  mutate(intervention = 'baseline')

support.auc <- support %>%
  group_by(run_id) %>%
  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
  mutate(intervention = 'Support')

noSupport.auc <- noSupport %>%
  group_by(run_id) %>%
  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
  mutate(intervention = 'NoSupport')

combined.auc <- rbind(base.auc, support.auc, noSupport.auc)
```

```{r}
print(combined.auc)

combined.auc.plot <- combined.auc %>%
  group_by(intervention) %>%
  summarise(sd = sd(AUC),
            se = sd / sqrt(n()),
            AUC = mean(AUC))

ggplot(data = combined.auc.plot, aes(x = intervention, y = AUC, group = intervention, fill = intervention)) +
  geom_col() +
  geom_errorbar(aes(ymin = AUC - se, ymax = AUC + se, width = 0.4, group = intervention)) +
  labs(title = 'Total AUC comparison', subtitle = 'Baseline vs Energy Crisis Interventions') +
  xlab('Intervention')
```

```{r}
# Another version showing difference from baseline for better comparison
combined.auc2 <- combined.auc %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('AUC')) %>%
  mutate(change_baseline = baseline - baseline,
         change_Support = Support - baseline,
         change_noSupport = NoSupport - baseline) %>%
  pivot_longer(cols = change_baseline:change_noSupport,
               names_to = 'intervention',
               names_prefix = 'change_',
               values_to = 'AUC_difference') %>%
  filter(intervention != 'baseline')

print(combined.auc2)

combined.auc2.plot <- combined.auc2 %>%
  group_by(intervention) %>%
  summarise(se = sd(AUC_difference) / sqrt(n()),
            AUC_difference = mean(AUC_difference))

ggplot(combined.auc2.plot, aes(x = intervention, y = AUC_difference, group = intervention, fill = intervention)) +
  geom_col() +
  geom_errorbar(aes(ymin = AUC_difference - se, ymax = AUC_difference + se, width = 0.4, group = intervention)) +
  labs(title = 'Change in AUC', subtitle = 'Baseline vs Energy Crisis Interventions') +
  xlab('Intervention')

ggplot(combined.auc2, aes(x = AUC_difference, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'Area Under Curve change by run')
```

@@

```{r}
combined.cost <- combined %>%
  #select(-pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
  select(run_id, year, alive_pop, total_boost, intervention, QALYs) %>%
  mutate(QALY_value = QALYs * 60000)

ggplot(combined.cost, aes(x = year, y = QALY_value, group = intervention, colour = intervention)) +
  geom_smooth() +
  scale_y_continuous(label = comma)

combined.cost.change <- combined.cost %>%
  select(-total_boost, -QALYs) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'QALY_value') %>%
  mutate(change_baseline = baseline - baseline,
         change_Support = energyDownlift - baseline,
         change_NoSupport = energyDownliftNoSupport - baseline) %>%
  select(-baseline, -energyDownlift, -energyDownliftNoSupport) %>%
  pivot_longer(cols = change_baseline:change_NoSupport,
               names_to = 'intervention',
               names_prefix = 'change_',
               values_to = 'QALY_value_change') %>%
  filter(intervention != 'baseline')

ggplot(combined.cost.change, aes(x = year, y = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
  geom_smooth() +
  scale_y_continuous(label = comma)

ggplot(combined.cost.change, aes(x = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  facet_wrap(~year) +
  labs(title = 'QALY value change')
```

```{r}
total.combined.cost <- combined.cost.change %>%
  group_by(run_id, intervention) %>%
  summarise(TotalChange = sum(QALY_value_change)) %>%
  group_by(intervention) %>%
  summarise(se = sd(TotalChange) / sqrt(n()),
            TotalChange = mean(TotalChange))

ggplot(total.combined.cost, aes(x = intervention, y = TotalChange, group = intervention, fill = intervention)) +
  geom_col() +
  geom_errorbar(aes(ymin = TotalChange - se, ymax = TotalChange + se, width = 0.4, group = intervention)) +
  scale_y_continuous(label = comma) +
  labs(title = 'Total Change in QALY Value', subtitle = 'Baseline vs Energy Crisis Interventions') +
  xlab('Intervention')
```

@@

```{r}
combined.cost.mean <- combined.cost %>%
  group_by(run_id, year, intervention) %>%
  summarise(across(everything(), mean))

# ICER = (C1 - C0) / (E1 - E0)
# where
# C1 = cost of intervention
# E1 = effect of intervention
# C0 = cost of control group
# E0 = effect of control group

ICER <- combined.cost.mean %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
  mutate(ICER_Support = (total_boost_energyDownlift - total_boost_baseline) / (QALYs_energyDownlift - QALYs_baseline),
         ICER_NoSupport = (total_boost_energyDownliftNoSupport - total_boost_baseline) / (QALYs_energyDownliftNoSupport - QALYs_baseline)) %>%
  select(run_id, year, ICER_Support, ICER_NoSupport) %>%
  pivot_longer(cols = -c(run_id, year),
               names_prefix = 'ICER_',
               names_to = 'intervention',
               values_to = 'ICER')

ggplot(ICER, aes(x = year, y = ICER, group = intervention, fill = intervention, colour = intervention)) +
  geom_smooth()

ICER.final <- ICER %>%
  group_by(run_id, intervention) %>%
  summarise(ICER = mean(ICER)) %>%
  group_by(intervention) %>%
  summarise(se = sd(ICER) / sqrt(n()),
            ICER = mean(ICER))

ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention)) +
  geom_col() +
  geom_errorbar(aes(ymin = ICER - se, ymax = ICER + se, width = 0.4, group = intervention)) +
  scale_y_continuous(label = comma) +
  labs(title = 'ICER', subtitle = 'Living Wage Intervention') +
  xlab('Intervention')
```

```{r}
ggplot(ICER, aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  facet_wrap(~year) +
  labs(title = 'ICER by run', subtitle = 'All Years')

ggplot(filter(ICER, year == 2022), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'ICER by run', subtitle = '2022')

ggplot(filter(ICER, year == 2028), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'ICER by run', subtitle = '2028')

ggplot(filter(ICER, year == 2031), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'ICER by run', subtitle = '2031')

ggplot(filter(ICER, year == 2034), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'ICER by run', subtitle = '2034')
```

>>>>

---
title: "QALY Comparisons - Energy Crisis Interventions - NoSupport Baseline"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

# combine the dataframes
combined <- rbind(support, noSupport)
```

@@

```{r}
ggplot(combined, aes(x = year, y = pop_boosted, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'Number Individuals Receiving Intervention')

combined.diff <- combined %>%
  select(run_id, year, intervention, total_boost) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'total_boost') %>%
  mutate(diff.boost = energyDownlift - energyDownliftNoSupport)

ggplot(combined.diff, aes(x = year, y = diff.boost)) +
  geom_smooth() +
  labs(title = 'Total Boost amount by year') +
  scale_y_continuous(label = comma)

@@

# Now change from baseline
combined.QALY.change <- combined %>%
  select(run_id, year, intervention, QALYs) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'QALYs') %>%
  mutate(QALYs = energyDownlift - energyDownliftNoSupport) %>%
  select(run_id, year, QALYs)

ggplot(data = combined.QALY.change, aes(x = year, y = QALYs)) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  geom_smooth() +
  labs(title = 'QALY change', subtitle = 'Support vs No Support')
```

@@

```{r}
auc.plots(base = noSupport, 
          base.name = 'NoSupport',
          intervention = support,
          int.name = 'Support')
```

@@

```{r}
cost.per.qaly(base = noSupport,
              base.name = 'energyDownliftNoSupport',
              int = support,
              int.name = 'energyDownlift',
              QALY_value = 60000)  # QALY value == £60,000
```

@@

```{r}
ICER(base = noSupport,
     base.name = 'energyDownliftNoSupport',
     int = support,
     int.name = 'energyDownlift',
     QALY_value = 60000)
```

### 2023-11-06 minos/testing/QALY_comparison_livingWage.Rmd
New visualisation script for comparing energyDownlift with energyDownliftNoSupport

```{r}
source(here::here('minos', 'utils_datain.R'))
```

@@

```{r}
# Another version showing difference from baseline for better comparison
combined.auc2 <- combined.auc %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('AUC')) %>%
  mutate(change_baseline = baseline - baseline,
         change_LivingWage = LivingWage - baseline) %>%
  pivot_longer(cols = change_baseline:change_LivingWage,
               names_to = 'intervention',
               names_prefix = 'change_',
               values_to = 'AUC_difference') %>%
  filter(intervention != 'baseline')

print(combined.auc2)

combined.auc2.plot <- combined.auc2 %>%
  group_by(intervention) %>%
  summarise(se = sd(AUC_difference) / sqrt(n()),
            AUC_difference = mean(AUC_difference))

ggplot(combined.auc2.plot, aes(x = intervention, y = AUC_difference, group = intervention, fill = intervention)) +
  geom_col() +
  geom_errorbar(aes(ymin = AUC_difference - se, ymax = AUC_difference + se, width = 0.4, group = intervention)) +
  labs(title = 'Change in AUC', subtitle = 'Baseline vs Living Wage Intervention') +
  xlab('Intervention')

ggplot(combined.auc2, aes(x = AUC_difference, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'Area Under Curve change by run')
```

>>>>

```{r}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_qaly.R'))
```

@@

```{r}
auc.plots(base = base, 
          base.name = 'baseline',
          intervention = wage,
          int.name = 'LivingWage')
```
